Digital economy in the UK: an evolutionary story

### 2023-02-16 paper/paper.Rmd
presentation

author_summary: |
  blah blah

bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
---

@@

@bednarz2020pulled
spatial innovation diffusion
By using Bayesian survival models with time-dependent data of wind turbine deployment
and firm foundation for 402 German regions between the years 1970 and 2015, we show that the spatial
evolution of the German wind energy industry was more strongly influenced by local demand–
pull than local supply–push processes.

The industry’s initial locations are distributed relatively arbitrarily
and unpredictably, as their needs in terms of resources and skills are diverse and distinct from the older existing
industries (Boschma and Lambooy, 1999). Consequently, emerging industries are characterized by relatively high
degrees of freedom in terms of location. In later extensions of the concept, the assumption of the randomness of locations
was revised with greater importance assigned to regional conditions (Boschma and Lambooy, 1999; Fornahl
et al., 2012).

larger local technological niches (at least from a demand perspective) are
more likely to be formed in urban areas than in rural ones, which is in line with the work of Ha¨gerstrand (1965a,b).
However, size is not the only regional characteristic that may matter in this context. Regions also differ in accumulated
experiences and the presence of tacit knowledge with respect to products, as well as in actors’ propensity share
this knowledge among producers (Martin et al., 2019)

@@

The
criticisms are mainly based on the fact that although the
approach gives an idea of aggregate (industry or household)
behaviour, it does not focus on the individual’s
(firm or household) adoption process

@@

Contagious diffusion=> spatial autocorelation

@@

The work by the communication sociologist Everett Rogers (1962, 1971, 1983) has emphasized the role of
information, communication, formal and informal media, opinion leaders and social networks, and economic
and psychological constraints on acceptance. Rogers’s work stresses the decision mechanism of the potential
adopter; the work of Rogers partitions the adopter’s process of choosing to accept a new phenomenon or
trait into five stages: stage 1–the potential adopter gains knowledge or awareness of an innovation; stage
2–persuasion is exercised to adopt; stage 3–a decision is made to adopt; stage 4–the decision to adopt is
implemented; stage 5–the adopter confirms the decision to adopt. In Rogers’s stage theory there may be a
substantial time lag between when a potential adopter becomes aware of the new characteristic and when a
decision is actually made to adopt.

@@

@zook2022mapping
Because new digital activities are rarely—if
ever—captured in official state data, researchers
must rely on information gathered from alternative
sources. With this in mind, the overarching aim of
this article is outlining an approach for analyzing the
“new spaces and geographies” of digital phenomena
and practices.

@@

Diffusion is a spatial (Hagerstrand, 1967) as well as a
temporal process, and historical evidence confirms that
technologies diffuse at different times, at different rates, and
to different extents in different places, and can be significantly
influenced by policies (Victor, 1993). An illustrative empirically
based theory for technology diffusion acrossmultiple regions is
suggested by “Schmidt's Law” (Grubler, 1990). With respect to a
specific technology, it divides regions into three groups: core,
rim, and periphery. The core iswhere the technology is invented,
subject to experimentation, and first deployed commercially.
To develop the technology, the core must have both sufficient
innovative ability and economic motivation to make the
necessary resource commitment. As the technology spreads
from the core to the rim and eventually to the periphery, later
adopters have the advantage of benefiting from the experiences
of earlier adopters via knowledge spillover effects (Verdolini and
Galeotti, 2011). At this point, the technology has likely been
refined and costs have likely declined significantly. Schmidt's
Law claims that, as a result, diffusion proceeds at a faster rate in
regions which adopt the technology later. However, diffusion
tends to be less pervasive in regions where adoption is delayed,
ultimately saturating at a lower extent than in regions where
adoption occurred earlier. This is often attributed to a lack of
proper institutions and infrastructures in later adopters, markets
whichmay not be as favorable to a technology, or the availability
of yet newer options that invite technological leapfrogging.

@@

Early on in their lifecycle, new technologies are crude, imperfect,
and expensive (Rosenberg, 1994). New energy technologies
are attractive for their ability to perform a particular task or
deliver a new or improved energy service (Fouquet, 2010). This is
often circumscribed by a particular set of needs in a particular
context: a market ‘niche’. End-users in niche markets are generally
less sensitive to the effective price of the energy service
provided or have a higher willingness to pay for its performance
advantages (Fouquet, 2010). Thus initially, performance dominates
cost competitiveness (Wilson and Grubler, 2011). Market
niches afford some protection from competitive pressures, allowing
technologies to be tested and improved in applied settings,
reducing uncertainties with performance or market demand
(Kemp et al., 1998). Costs may only fall substantively after an
extended period of commercial experimentation, concurrent with
the establishment of an industrial base and characteristic moves
towards standardisation and mass production (Grubler, 1998).
The influence of accumulating production experience on costs is
captured by the concept of learning.

@@

The scale of spatial innovation diffusion is similar* to that of
temporal diffusion models: hierarchically decomposed.

@@

Hagerstrand (1968) was the first
to demonstrate that diffusion typically starts from innovative centers
(‘core´) and disseminates, through a hierarchy of subcenters, to the
periphery. This process is sequential rather than simultaneous, and
tends to accelerate from core to periphery, where diffusion reaches a
lower intensity than in the core (Hagerstrand, 1968; Grubler, 1990;
Morrill, 2005). A similar effect of spatial acceleration has been identified
in marketing research and is known as the “lead-lag effect” (Peres
et al., 2010).

@@

Geographers, of course, were at the forefront of
quantitative diffusion research. Ha¨gerstrand’s (1967)
early work on understanding innovation diffusion in
Sweden using simulation modeling is particularly noteworthy
in this respect. However, already long before the
‘‘cultural turn’’ in economic geography (Barnes 2001),
geographers’ interest in formally modeling the diffusion
of new innovations waned (Gregory 1985). Indeed,
much of the recent quantitative research into the diffusion
of new technology has been undertaken by
economists, sociologists, and business scholars.

@@

The first involves a country’s geographical location.
Recent empirical work suggests that diffusion is ‘‘geographically
localized’’ (Globerman, Kokko, and Sjo¨holm
2000; Keller 2002; Milner 2003) in that a technology
diffuses faster in a country where it is already more
widely diffused in neighboring countries. Underlying
these regional effects are contagion and contact with
prior users or producers of technology.

@@

Hägerstrand (1952, 1967) was the first scholar to intensively analyze spatial diffusion pro
cesses.
Based on the empirical observations of the regional spread of process innovations,
he hypothesized that new technology is first implemented in the ‘center’ – the large agglom
erations
– and then moves ‘down’ the spatial hierarchy, the last stop being the ‘periphery’,
i.e. remote and sparsely populated regions. There are at least two factors that may explain
this pattern: first, the transfer of tacit knowledge via face-to-face contact and second, the
absorptive capacity of a region.

# Literature review {#sec2} MAYBE SKIP THIS??

@@

from R: Asym/(1+exp((xmid-input)/scal))
using the terms from Wilson k/(1 + e^(t_0 - t)/scal)

Wilson: k(1 + e^-b(t - t_0))
So, scal = - 1/b

The curve is symmetric* around t_0

>>>>

author_summary: |
  blah blah
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
editor_options: 
  markdown: 
    wrap: 72
---

@@

@bednarz2020pulled spatial innovation diffusion By using Bayesian
survival models with time-dependent data of wind turbine deployment and
firm foundation for 402 German regions between the years 1970 and 2015,
we show that the spatial evolution of the German wind energy industry
was more strongly influenced by local demand-- pull than local
supply--push processes.

The industry's initial locations are distributed relatively arbitrarily
and unpredictably, as their needs in terms of resources and skills are
diverse and distinct from the older existing industries (Boschma and
Lambooy, 1999). Consequently, emerging industries are characterized by
relatively high degrees of freedom in terms of location. In later
extensions of the concept, the assumption of the randomness of locations
was revised with greater importance assigned to regional conditions
(Boschma and Lambooy, 1999; Fornahl et al., 2012).

larger local technological niches (at least from a demand perspective)
are more likely to be formed in urban areas than in rural ones, which is
in line with the work of Ha¨gerstrand (1965a,b). However, size is not
the only regional characteristic that may matter in this context.
Regions also differ in accumulated experiences and the presence of tacit
knowledge with respect to products, as well as in actors' propensity
share this knowledge among producers (Martin et al., 2019)

@@

The criticisms are mainly based on the fact that although the approach
gives an idea of aggregate (industry or household) behaviour, it does
not focus on the individual's (firm or household) adoption process

@@

Contagious diffusion=\> spatial autocorelation

@@

The work by the communication sociologist Everett Rogers (1962, 1971,
1983) has emphasized the role of information, communication, formal and
informal media, opinion leaders and social networks, and economic and
psychological constraints on acceptance. Rogers's work stresses the
decision mechanism of the potential adopter; the work of Rogers
partitions the adopter's process of choosing to accept a new phenomenon
or trait into five stages: stage 1--the potential adopter gains
knowledge or awareness of an innovation; stage 2--persuasion is
exercised to adopt; stage 3--a decision is made to adopt; stage 4--the
decision to adopt is implemented; stage 5--the adopter confirms the
decision to adopt. In Rogers's stage theory there may be a substantial
time lag between when a potential adopter becomes aware of the new
characteristic and when a decision is actually made to adopt.

@@

@zook2022mapping Because new digital activities are rarely---if
ever---captured in official state data, researchers must rely on
information gathered from alternative sources. With this in mind, the
overarching aim of this article is outlining an approach for analyzing
the "new spaces and geographies" of digital phenomena and practices.

@@

Diffusion is a spatial (Hagerstrand, 1967) as well as a temporal
process, and historical evidence confirms that technologies diffuse at
different times, at different rates, and to different extents in
different places, and can be significantly influenced by policies
(Victor, 1993). An illustrative empirically based theory for technology
diffusion acrossmultiple regions is suggested by "Schmidt's Law"
(Grubler, 1990). With respect to a specific technology, it divides
regions into three groups: core, rim, and periphery. The core iswhere
the technology is invented, subject to experimentation, and first
deployed commercially. To develop the technology, the core must have
both sufficient innovative ability and economic motivation to make the
necessary resource commitment. As the technology spreads from the core
to the rim and eventually to the periphery, later adopters have the
advantage of benefiting from the experiences of earlier adopters via
knowledge spillover effects (Verdolini and Galeotti, 2011). At this
point, the technology has likely been refined and costs have likely
declined significantly. Schmidt's Law claims that, as a result,
diffusion proceeds at a faster rate in regions which adopt the
technology later. However, diffusion tends to be less pervasive in
regions where adoption is delayed, ultimately saturating at a lower
extent than in regions where adoption occurred earlier. This is often
attributed to a lack of proper institutions and infrastructures in later
adopters, markets whichmay not be as favorable to a technology, or the
availability of yet newer options that invite technological
leapfrogging.

@@

Early on in their lifecycle, new technologies are crude, imperfect, and
expensive (Rosenberg, 1994). New energy technologies are attractive for
their ability to perform a particular task or deliver a new or improved
energy service (Fouquet, 2010). This is often circumscribed by a
particular set of needs in a particular context: a market 'niche'.
End-users in niche markets are generally less sensitive to the effective
price of the energy service provided or have a higher willingness to pay
for its performance advantages (Fouquet, 2010). Thus initially,
performance dominates cost competitiveness (Wilson and Grubler, 2011).
Market niches afford some protection from competitive pressures,
allowing technologies to be tested and improved in applied settings,
reducing uncertainties with performance or market demand (Kemp et al.,
1998). Costs may only fall substantively after an extended period of
commercial experimentation, concurrent with the establishment of an
industrial base and characteristic moves towards standardisation and
mass production (Grubler, 1998). The influence of accumulating
production experience on costs is captured by the concept of learning.

@@

The scale of spatial innovation diffusion is similar\* to that of
temporal diffusion models: hierarchically decomposed.

@@

Hagerstrand (1968) was the first to demonstrate that diffusion typically
starts from innovative centers ('core´) and disseminates, through a
hierarchy of subcenters, to the periphery. This process is sequential
rather than simultaneous, and tends to accelerate from core to
periphery, where diffusion reaches a lower intensity than in the core
(Hagerstrand, 1968; Grubler, 1990; Morrill, 2005). A similar effect of
spatial acceleration has been identified in marketing research and is
known as the "lead-lag effect" (Peres et al., 2010).

@@

Geographers, of course, were at the forefront of quantitative diffusion
research. Ha¨gerstrand's (1967) early work on understanding innovation
diffusion in Sweden using simulation modeling is particularly noteworthy
in this respect. However, already long before the ''cultural turn'' in
economic geography (Barnes 2001), geographers' interest in formally
modeling the diffusion of new innovations waned (Gregory 1985). Indeed,
much of the recent quantitative research into the diffusion of new
technology has been undertaken by economists, sociologists, and business
scholars.

@@

The first involves a country's geographical location. Recent empirical
work suggests that diffusion is ''geographically localized'' (Globerman,
Kokko, and Sjo¨holm 2000; Keller 2002; Milner 2003) in that a technology
diffuses faster in a country where it is already more widely diffused in
neighboring countries. Underlying these regional effects are contagion
and contact with prior users or producers of technology.

@@

Hägerstrand (1952, 1967) was the first scholar to intensively analyze
spatial diffusion pro cesses. Based on the empirical observations of the
regional spread of process innovations, he hypothesized that new
technology is first implemented in the 'center' -- the large agglom
erations -- and then moves 'down' the spatial hierarchy, the last stop
being the 'periphery', i.e. remote and sparsely populated regions. There
are at least two factors that may explain this pattern: first, the
transfer of tacit knowledge via face-to-face contact and second, the
absorptive capacity of a region.

# Literature review {\#sec2} MAYBE SKIP THIS??

@@

from R: Asym/(1+exp((xmid-input)/scal)) using the terms from Wilson k/(1
+ e\^(t_0 - t)/scal)

Wilson: k(1 + e\^-b(t - t_0)) So, scal = - 1/b

The curve is symmetric\* around t_0

### 2023-02-16 presentations/gceg.Rmd
presentation

```{r, echo=FALSE, results=FALSE, include=FALSE}
library(knitr)
library(rprojroot)

@@

# This is the project path
path <- find_rstudio_root_file()

#bibliography: ../bibliography.bib
```

## Contents
- Introduction
- Web data and spatial research
- Empirical strategy
- Descriptive statistics
- Results
- Conclusions
<br>
<br>
[etranos.info/post/sad2021](https://etranos.info/post/sad2021)

@@

- Map the active engagement with the *digital*
- Over time, early stages of the internet
- Granular spatial level
- Importance: understand how the adoption of technologies evolves
- Predictions of introduction times for future technologies [@meade2021modelling]

@@

## Diffusion

Large scale adoption studies

Add Figure

## Spatiality of the internet using supply-side measures

- Map internet infrastructure, *both*:

  - backbone (ADD REF), and

  - last mile (ADD REF, Singleton, Hannah)

- Economic effects:

  - Kolko

  - Nathan

## ???

@beardsell1999spatial used the employment in the computer industry to assess
its evolution

# Results

@@

```{r results='asis', out.width = "60%"}

library(magick)
library(purrr)
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir

@@

```{r results='asis', out.width = "60%"}

library(magick)
library(purrr)
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex_log1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir

```{r eval=FALSE, fig.show='animate', ffmpeg.format='gif', dev='jpeg', interval=0.01}

hex.images <- list.files(path = path.images, pattern = "^hex", full.names = T)
for (i in hex.images){
  plot(i) # for example
}
```

>>>>

```{r, echo=FALSE, results=FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(rprojroot)
library(magick)
library(purrr)
library(kableExtra)

@@

# This is the project path
path <- find_rstudio_root_file()
```

## Contents
<br>
<div style="margin-left: 50px !important; text-align:left !important">
- Introduction
- Web data
- Spatial analysis
- S-shaped diffusion curves
- Conclusions
<br>
<br>
[etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/)
</div>

@@

<br>

- Map the **active** engagement with the *digital*
- Over time, **early stages** of the internet
- **Granular** and **multi-scale** spatial perspective

## Importance

- Understand how the adoption of new technologies evolves

- Guide policies for deployment of new technologies

- Predictions of introduction times for future technologies [@meade2021modelling]:

@@

## Technological diffusion

<br>

![](images/S-shaped-logistic-diffusion-curve_W640.jpg)

## *Spatial* diffusion processes

- As in temporal diffusion models, an **S-shaped** pattern in the
cumulative level of adoption

- A **hierarchy effect**: from main centers to secondary ones -- central places

- A **neighborhood effect**: diffusion proceeds outwards from innovation centers, 
first "hitting" nearby rather than far-away locations [@grubler1990rise]

@hagerstrand1965monte: from innovative centers (core) through a
hierarchy of subcenters, to the periphery

## Internet geographies

- Map internet infrastructure

  - backbone [@malecki2002economic; @tranos2013geography]

  - last mile [@riddlesden2014broadband; @budnitz2022working]

- Social media and user generated content

  - Here and now effect [@crampton2013beyond]

> Because new digital activities are rarely---if
ever---captured in official state data, researchers must rely on
information gathered from alternative sources [@zook2022mapping].

# Web data

## Web data: The Internet Archive
- The largest archive of webpages in the world
- 273 billion webpages from over 361 million websites, 15 petabytes of storage (1996 -)
- A web crawler starts with a list of URLs (a seed list) to crawl and downloads a copy of their content
- Using the hyperlinks included in the crawled URLs, new URLs are identified and crawled (snowball sampling)
- Time-stamp

## Web data: The Internet Archive
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/figure/Picture1.png){width=70%}

## Web data: The Internet Archive
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/figure/Picture2.png){width=70%}

## Our web data
- JISC UK Web Domain Dataset: all archived webpages from the .uk domain 1996-2012

- Curated by the British Library

<small>

- Tranos, E., and C. Stich. 2020. Individual internet usage and the availability of online content of local interest: A multilevel approach. *Computers, Environment and Urban Systems*, 79:101371.

- Tranos, E., T. Kitsos, and R. Ortega-Argilés. 2021. Digital economy in the UK: Regional productivity effects of early adoption. *Regional Studies*, 55:12, 1924-1938.

- Stich, C., E. Tranos and M. Nathan. 2022. Modelling clusters from the ground up: a web data approach. *Environment and Planning B*, in press.

- Tranos, E., A. C. Incera and G. Willis. 2022. Using the web to predict regional trade flows: data extraction, modelling, and validation, *Annals of the AAG*, in press.

</small>

## Our web data

- All .uk archived webpages which contain a UK postcode in the web text

- Circa 0.5 billion URLs with valid UK postcodes

<br>
<br>

<!-- <small></small> -->
20080509162138/http://www.website1.co.uk/contact_us IG8 8HD

## Data cleaning

- All the archived .uk webpages

- Archived during 1996-2012

- Commercial webpages (.co.uk)

- From webpages to websites:

    <small>- http://www.website1.co.uk/webpage1 and</small>

    <small>- http://www.website1.co.uk/webpage2 are part of the</small>

    <small>- http://www.website1.co.uk</small>

- 1 *vs.* multuple postcodes in a website

## Unique postcodes frequencies, 2000

```{r eval=TRUE, echo=FALSE, results='asis'}

# load 2000 co.uk
# setwd("C:/Users/TranosE/DataShare/archive/nuts")
path.2000 <- "C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/all2000couk.csv"

all2000.duplicates <- data.table::fread(path.2000) #
# dim(all2000.duplicates) # 3336162
# it includes duplicated URLs: if one webpages includes multiple postcodes
# then it appears multiple times. This is ok for the nuts aggregation, but
# not for the frequencies
# This is only .co.uk

# one line for every host
all2000 <- unique(all2000.duplicates, by = c("host")) # 57897

# unique postcodes per website f table
f.websites.pc <- DescTools::Freq(all2000$V1, breaks = c(0, 1,2, 10,100,1000,10000,100000), ord = "desc")
f.websites.pc$level <- factor(f.websites.pc$level, levels = c("[0,1]","(1,2]", "(2,10]", "(10,100]",
                                                              "(100,1e+03]", "(1e+03,1e+04]",
                                                              "(1e+04,1e+05]"))
levels(f.websites.pc$level) <- c("(0,1]","(1,2]", "(2,10]", "(10,100]", "(100,1000]", "(1000,10000]", "(10000,100000]")
kable(f.websites.pc,
      format = "html",
      digits = 3,
      format.args = list(big.mark = ",")) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```
<br>

- Websites with a large number of postcodes: e.g. directories, real estate websites

- Focus on websites with **one unique** postcode per year

## Directory website with a lot of postcodes
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

## Website with a unique postcode in London
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

# Analysis

## Mapping website density

@@

```{r heatmaps, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

```{r heatmaps_log, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex_log1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

## Spatial attributes

<br>

Two scales:

- Output areas (c. 200,000)

- Local authorities (c. 400)

<br>

**Neighborhood effect**: diffusion proceeds outwards from innovation centers, 
first "hitting" nearby rather than far-away locations [@grubler1990rise]

- Moran's I

- LISA maps

- Website density regressions

```{r moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

read.csv(path.in) %>% dplyr::select(year, morani) %>% 
  ggplot(aes(x=year, y=morani)) +
  geom_bar(stat = "identity") + 
  ylab('Moran\'s I') +
  theme_minimal() +
  ggtitle("Moran\'s I, number of websites per Output Areas") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/morani_la.csv")

read.csv(path.in) %>% dplyr::select(year, morani) %>% 
  ggplot(aes(x=year, y=morani)) +
  geom_bar(stat = "identity") + 
  ylab('Moran\'s I') +
  theme_minimal() +
  ggtitle("Moran\'s I, number of websites per Local Authority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

```{r lisa_oa, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^lisa_level_pc1_oa", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^lisa_level_pc1_la", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

## Website density regressions

<br>

$$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$

<br>

<div style="margin-left: 50px !important; text-align:left !important">
$Place$:

- London, *or*

- Nearest city, *or*

- Nearest retail centre

$i$: Output Areas *or* Local Authorities
</div>

## Website density regressions

<br>

$\beta$ interpretation:

- The lower the $\beta$ is (or the larger the $|\beta|$ is)...

- ... the larger urban gravitation is for web adoption.

```{r b_London_oa, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

```{r b_London_la, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/b_dist_london_la.png")
knitr::include_graphics(path.image)
```

```{r b_city_oa, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

```{r b_city_la, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_la.png")
knitr::include_graphics(path.image)
```

```{r b_centre_oa, message=FALSE, out.height= "60%", out.width="60%"}
#fig.height=4, fig.width=4, 
path.image <- paste0(path, "/outputs/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

```{r b_centre_la, message=FALSE, out.height= "60%", out.width="60%"}
path.image <- paste0(path, "/outputs/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

```{r r_squared, eval=F, results='asis'}
# This is for the RSquared of the different website density regressions.
# The RSquared does not drop much hence it is not worth reporting.

path.in1 <- paste0(path, "/outputs/r2_all_oa.csv")
path.in2 <- paste0(path, "/outputs/r2_all_la.csv")

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  ggplot(aes(x=year)) +
  geom_line(aes(y=London, color = "OA to London"), size=1) +
  geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
  geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +

  geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) +
  geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) +
  geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) +

  scale_color_discrete(name = "Website density regressions") +
  scale_linetype_manual(name = "Website density regressions") +
  theme_minimal()

  scale_color_manual(values = c("red", "blue", "green"))

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  pivot_longer(names_to = "destinations",
               values_to = "Rsquared",
               cols = 2:7) %>% 
  arrange(destinations, year) %>% 
  ggplot(aes(x=year)) +
  geom_line(aes(y=Rsquared, group=destinations, colour=destinations)) +
  geom_textline(aes(y=Rsquared, group=destinations, colour=destinations, 
                    label=destinations),
                hjust = 1) +
  theme(legend.position = "none") +
  theme_minimal()

@@

<br>

**Hierarchy effect**: from main centers to secondary ones -- central places

- Gini coefficient

```{r gini_oa, results='asis'}
path.in <- paste0(path, "/outputs/gini_oa.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, number of websites per Output Area") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

```{r gini_la, results='asis'}
path.in <- paste0(path, "/outputs/gini_la.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, number of websites per Local Auhtority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

## Spatial attributes, a summary

- Spatial dependency relatively small and constant over time / scales

- At local scale, consistent hotspots over time

- More granular analysis reveals hotspots

- Almost perfect polarisation of web adoption in the early stages at a granular level

- More equally diffused at the Local Authority level

- Plateau overtime

- Distance effect: urban gravitation increases over time and then drops

- Consistent across scales and definitions of urban

# S-shaped diffusion curves

```{r UK S, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_uk.png")
knitr::include_graphics(path.image)
```

```{r LA_S_gif, eval=F, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

library(magick)
las <- list.files(path = path.images, pattern = "^lad_", full.names = T) #%>% 
las_list <- lapply(las, image_read)

## join the images together
las_joined <- image_join(las_list)

## animate at 2 frames per second
las_animated <- image_animate(las_joined, fps = 2)

## view animated image
las_animated

## save to disk
image_write(image = las_animated,
            path = "las.gif")

  # map(image_read) %>% # reads each path file
  # image_join() %>% # joins image
  # image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

```{r Xmid_frequency_graph, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/xmid_f.png")
knitr::include_graphics(path.image)
```

```{r diffusion_speed_map, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/speed_pam.png")
knitr::include_graphics(path.image)
```

<!-- fast  -->

```{r Darlington, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000005.png")
knitr::include_graphics(path.image)
```

```{r Nottingham, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000018.png")
knitr::include_graphics(path.image)
```

```{r Reading, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000038.png")
knitr::include_graphics(path.image)
```

```{r City_of_London, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E09000001.png")
knitr::include_graphics(path.image)
```

<!-- slow -->

```{r Middlesbrough, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000002.png")
knitr::include_graphics(path.image)
```

```{r Leicester, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000016.png")
knitr::include_graphics(path.image)
```

```{r Bristol, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000023.png")
knitr::include_graphics(path.image)
```

```{r Plymouth, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000026.png")
knitr::include_graphics(path.image)
```

```{r Liverpool, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E08000012.png")
knitr::include_graphics(path.image)
```

```{r Hackney, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E09000012.png")
knitr::include_graphics(path.image)
```

```{r Edinburgh, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_S12000036.png")
knitr::include_graphics(path.image)
```

# Conclusions

## What have we learned?

- **Geography matters:** spatial dependency, urban gravitation

- Some indications of a hierarchical diffusion

- Granular analysis reveals patterns otherwise not visible

- Well-established theoretical approaches of diffusion survive even at a granular level

## What have we *yet* to learn?

- Explain the spatial patterns of fast/slow web adoption

  - Applied the same analysis fo OA

  - Survival regressions [@perkins2005international]

- Expand our definition of web to websites with # of postcodes > 1
